Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-09 Paper/paper.tex
Update text

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
  Universit\"at Potsdam, Karl-Liebknecht-Str.\ 24/25, 14476 Potsdam,
  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
  Santa Barbara, CA 93106-9530 USA}
% Update Gabor's address to Potsdam
\date{Accepted ---. Received ---; in original form ---}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[scale=0.65]{emissivity.pdf}
    % gammapi.py -- draw_emissivity() 
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude.  Brown points show the
    emissivity when the best-fit double power law luminosity functions
    at respective redshifts are integrated down to $M_{1450}=-18$.
    Black points show the integration limit when the limit is assumed
    to be $M_{1450}=-21$.  For comparison, various other published
    models of the 1~Ry emissivity of AGN are also shown.  The blue
    curve in these panels shows the AGN 912~\AA\ emissivity model of
    \citet{2012ApJ...746..125H}, which is very similar to the model of
    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
    determination from the fits of \citet{2015AA...578A..83G}.  The
    maroon curve is the published fit to the 1~Ry emissivity evolution
    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
      HM12 Lstar limits.  Mention that Akiyama open and filled circles
      are very close.}}
  \label{fig:e912}
\end{figure*}

@@

Figure~\ref{fig:e912} show the resultant 1~Ry emissivity when the

@@

We fit this to the points shown in Figure~\ref{fig:e912} assuming a

@@

shown in both panels of Figure~\ref{fig:e912}.  We now comment on the

@@

and closed brown circles at $z=0$ in Figure~\ref{fig:e912}.  Our

@@

The brown dashed curve in Figure~\ref{fig:e912} shows the AGN 1~Ry
emissivity model of \citet{2012ApJ...746..125H}, which based on the
bolometric luminosity function model of \citet{2007ApJ...654..731H}.
Their assumed emissivity agrees reasonably well with our
$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912}
shows the model presented by \citet{2015ApJ...813L...8M}.  This model
disagrees with ours rather severely at almost all redshifts in the
range considered here.  Note that a direct comparison with
\citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M} is
difficult because these models integrate the luminosity function to a
fixed fraction of the break luminosity $L_*$ instead of a fixed
absolute magnitude.  The chosen limite by \citet{2012ApJ...746..125H}
and \citet{2015ApJ...813L...8M} is $0.01L_*$.  Using a limit that
depends on the break luminosity can be problematic as different quasar
surveys used to develop these emissivity models often report
strikingly different break luminosity values.  Even when these samples
are homogeneized appropriately, have such an integration limit is only
justified if the faint-end slope of the luminosity function is
sufficiently shallow.

The grey dashed curve shows the emissivity model of
\citet{2017MNRAS.466.1160M}.  These authors integrate the luminosity
function down to $M_{1450}=-19$.  However, their model strongly
disagrees with our inference, potentially due to biases resulting from
combining binned luminosity function estimates from different sources
inhomogeneously.  The green curves in Figure~\ref{fig:e912} show the
luminosity function derived from a variability-selected sample
observed using the Sloan telescope and the Multiple Mirror Telescope
(MMT) by \citet{2013A&A...551A..29P}.  This sample of 1877 quasars
does not overlap with the variability-selected sample reported by the
BOSS survey \citep{2013ApJ...773...14R}.  \citet{2013A&A...551A..29P}
assum constant luminosity function slopes with a break at $z=2.2$ and
assume a pure luminosity evolution.  This leads to a discontinuity in
the emissivity evolution in their model at $z=2.2$.  We convert their
$g$-band magnitudes to $M_{1450}$ and integrate the resultant
luminosity function down to our two chosen integration limits.  The
result is shown in Figure~\ref{fig:e912} by the solid and dashed
orange curves, which correspond to $M_{1450}<-21$ and $-18$,
respectively.  For $M_{1450}<-21$, our models are in reasonable
agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
models disagree by 10--30\%.  Figure~\ref{fig:e912} also shows the
model presented by \citet{2016A&A...587A..41P}.  We consider their
PLE$+$LEDE model, in which the faint-end slope is assumed to stay
constant with redshift.  Although the emissivity evolution in this
model is continuous at $z=2.2$, it is not smooth.  This model agrees
with our $M_{1450}<-18$ result to a better degree relative to the
\citet{2013A&A...551A..29P} model.  We also compare our result with
the PLE$+$LEDE luminosity function model presented by
\citet{2017A&A...608A..64C} by reanalysing the
\citet{2016A&A...587A..41P} sample with an improved $K$-correction
implementation.  \citet{2017ApJ...847L..15O} recently fit a double
power law luminosity function model to a combined binned samples of
\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
photometric redshift $z\sim 6$ reported by
\citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
orange rectangle in Figure~\ref{fig:e912}.  The lower side of the
rectangle corresponds to the emissivity for the
\citet{2017ApJ...847L..15O} model excluding the
\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
the emissivity is higher; this is shown by the upper end of the
rectangle.  The open rectangle corresponds to $M_{1450}<-18$ and the
closed rectangle corresponds to $M_{1450}<-21$.

The red open cirles with error bars in Figure~\ref{fig:e912} show the
determination from the fits of \citet{2015AA...578A..83G}.  These
authors also choose a break luminosity-dependent integration limit of
$0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their model.
The resultant emissivities are factors of 2 to 3 higher than our
determinations for $z=4$--$6$.  This is puzzling at first sight,
because the AGN candidates reported by \citet{2015AA...578A..83G} are
consistent with our luminosity function estimates obtained without
these candidates (see Appendix~\ref{sec:conv}).  Our luminosity
function are also somewhat steeper than those reported by
\citet{2015AA...578A..83G}.  The discrepancy is explained by the
difference in the two luminosity function models at intermediate
magnitudes.  We find that the data prefer a much brighter break
luminosity than that infered by \citet{2015AA...578A..83G}.  This
reduces our emissivities relative to their estimates.  We go into this
issue in further detail in Appendix~\ref{sec:conv}.

\citet{2018AJ....155..131M} recently extended their previous Stripe~82
AGN sample by 1.5 magnitude and fit a double power law luminosity
function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
LF to our cosmology and assumed our SED obtain the emissivities shown
by the green circles in Figure~\ref{fig:e912}.  Again the open and
filled circles corresponds to our two integration limits.  Our
emissivity agrees with the measurement of \citet{2018AJ....155..131M}
for $M_{1450}<-21$ but is higher than their measurement for
$M_{1450}<-18$, which is not surprising due to the difference in the
luminosity function slopes.  The emissivity derived from the
luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
in Figure~\ref{fig:e912}.  These authors report 1668 AGN candidates at
$3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
faint-end slope is very flat ($\beta=-1.3\pm 0.05$), inconsistent with
our determination at all redshifts.  Their inferred emissivity is
consistent with our estimate for $M_{1450}\sim -21$.  Their emissivity
does not change significantly with the integration limit thanks to the
shallow slope.  We also compare our emissivities with the
determinations reported by \citet{2012ApJ...755..169M} at $z\sim 3.2$
and $z\sim 4$.  Their emissivity in reasonably agreement with our
model for $M_{1450}<-21$ at $z\sim 3.2$.  But their $M_{1450}<-18$
emissivity disagrees with all other high-redshift estimates, possibly
indicating a systematic error.  Our emissivity estimates are in good
agreement with those of \citet{2018MNRAS.474.2904P}.  Mention
Bongiorno.

@@

\subsection{Photon underproduction at $z=0$?}

Our derivation of the LyC emissivity of AGN allows us to see if the
corresponding hydrogen photoionization rate is consistent with the
measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
\gk{Define acronym CDDF.}  these redshifts, hydrodynamical
cosmological simulations require a hydrogen photoionization rate that
is a factor of five larger than that in the UV background (UVB) model
of \citet{2012ApJ...746..125H}.  \gk{This factor looks more than five
  in our plot!}  Several recent studies in the literature have
addressed this ``photon underproduction crisis''.  On the one hand,
these studies emphasised the uncertainty in the
\citet{2012ApJ...746..125H} UVB model at these redshifts due to the
lack of certainty in the UV photon emissivities of galaxies and AGN
\citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.  On the other hand,
they noted the uncertainty in the results of the cosmological
simulations at these redshifts, due to effects such as AGN feedback
and limited numerical resolution \citep{2015ApJ...811....3S,
  2017MNRAS.467L..86V, 2017MNRAS.471.1056N, 2017ApJ...837..106O,
  2017MNRAS.466..838G, 2017MNRAS.467.3172G, 2017ApJ...835..175G}.  A
general conclusion of these studies was that the discrepancy between
the photoionization rate required by the observed CDDF and predicted
by the UVB model of \citet{2012ApJ...746..125H} is likely to be
smaller than that found by \citet{2014ApJ...789L..32K}.  The
discrepancy is about a factor of 2 instead of 5.

\begin{figure}
  \begin{center}
    % rtg2.draw_g_puc()
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Evolution of the hydrogen photoionisation rate at low
    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
\end{figure}

The black curve in Figure~\ref{fig:puc} shows the evolution of the
hydrogen photoionization rate due to AGN in our best-fit global
luminosity function model.  (Yellow shaded region around the black
curve shows the small 68\% uncertainty.)  We find that the
photoionisation rate in our model due to AGN alone is higher than that
in the \citet{2012ApJ...746..125H} UVB model by a factor of 2.  This
higher photoionisation rate is consistent with that derived by
\citet{2015MNRAS.451L..30K} using the quasar luminosity function
measurements of \citet{2009MNRAS.392...19C} and
\citet{2013A&A...551A..29P}.  It is also consistent with the
photoionization rate found by \citet{2017MNRAS.467.3172G}, who found
that this photoionisation rate is sufficient to explain the CDDF
measured by \citet{2016ApJ...817..111D}.

\gk{Add discussion about Schulze point from Gabor's 8 March email
  here.}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Evolution of the \HeIII\ ionization fraction in our model,
    when the AGN luminosity function is integrated down to
    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
    (red curve and shaded region).  The shaded regions show the
    one-sigma (68.26\%) uncertainty.  Other curves show models of
    \citet[solid grey]{2012ApJ...746..125H}, \citet[dashed
      grey]{2015ApJ...813L...8M}, \citet[brown with shaded
      region]{2016ApJ...828...90L}, \citet[blue]{2018arXiv180104931P},
    \citet[maroon]{2009ApJ...694..842M}, and
    \citet[green]{2014MNRAS.445.4186C}.  Note that we derive
    $Q_\nHeIII$ using Equation~(\ref{eqn:qHedot}), which ignores the
    presence of \HeII\ Lyman-limit systems and becomes inaccurate
    towards $Q_\nHeIII\sim 1$. \label{fig:qhe}}
\end{figure}

@@

\section{Comparison with G15}
\label{sec:conv}
%% Define 'G15' somewhere above.
In the double power law luminosity function models presented in
distinct redshift bins in Section~\ref{sec:bins}, we did not include
the 19 low-luminosity ($M_{1450}>-22.6$) AGN between redshifts $z=4.1$
and $6.3$ reported by G15.  While this was done in order to restrict
our sample to quasars with spectroscopic redshift determinations, it
is instructive to consider how our results are affected if the G15 AGN
are added to the analysis.  In their work, G15 found a shallower
faint-end slope ($\beta\sim -1.5$ to $-1.8$) for the luminosity
function at $4.1 < z < 6.3$, relative to our result from other AGN
samples at these redshifts ($\beta\sim -2.0$ to $-2.5$).  Still, G15
derived a higher 912\,\AA\ emissivity than our estimates
(cf.\ Figure~\ref{fig:e912}), so that in their analysis AGN can
produce all ionizing photons necessary to keep hydrogen ionized and
explain the \lya data.  The black points in
Figure~\ref{fig:params_giallongo} show the parameters of the double
power law luminosity function from our analysis of
Section~\ref{sec:bins}.  The red open circles show the parameter
values obtained when the G15 sample is added to the analysis.  We find
that the two results are highly consistent, showing that the G15
sample is consistent with our double power law fit obtained from other
AGN samples are comparable redshifts.  This is surprising as the
integrated 912\,\AA\ emissivities in our model are smaller than those
derived by G15.  Figure~\ref{fig:lf_giallongo} provides an
explanation.  As seen in this figure, the double power law fits
favoured by G15 (red dashed curves) are quite different from our fits
(black curves).  The characteristic luminosity $M_*$ obtained by G15
is much fainter ($\sim -23$ at $z = 5$) than that resulting out of our
analysis ($\sim -29$ at $z = 5$).  Thus the 912\,\AA\ emissivities are
enhanced in G15 because of the increase contribution from
intermediate-luminosity AGN in their model.
Figure~\ref{fig:lf_giallongo} suggests that this is possibly because
of the inclusion of SDSS Stripe 82 data from
\citet{2013ApJ...768..105M} and the AGN samples of
\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in our
analysis.  Additionally, the homogenisation of data in our work may
also cause part of the difference.

>>>>

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
  Universit\"at Potsdam, Karl-Liebknecht-Str.\ 24/25, 14476 Potsdam,
  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
  Santa Barbara, CA 93106-9530 USA}
\date{Accepted ---. Received ---; in original form ---}

@@

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[scale=0.65]{emissivity.pdf}
%%     % gammapi.py -- draw_emissivity() 
%%   \end{center}
%%   \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
%%     fraction down to a limiting magnitude.  Brown points show the
%%     emissivity when the best-fit double power law luminosity functions
%%     at respective redshifts are integrated down to $M_{1450}=-18$.
%%     Black points show the integration limit when the limit is assumed
%%     to be $M_{1450}=-21$.  For comparison, various other published
%%     models of the 1~Ry emissivity of AGN are also shown.  The blue
%%     curve in these panels shows the AGN 912~\AA\ emissivity model of
%%     \citet{2012ApJ...746..125H}, which is very similar to the model of
%%     \citet{2007ApJ...654..731H}.  Red circles with error bars show the
%%     determination from the fits of \citet{2015AA...578A..83G}.  The
%%     maroon curve is the published fit to the 1~Ry emissivity evolution
%%     in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
%%     the model of \citet{2015ApJ...813L...8M}.  The grey and brown
%%     curves show the best-fit form of Equation XX. \gk{Mention MH15 and
%%       HM12 Lstar limits.  Mention that Akiyama open and filled circles
%%       are very close.}}
%%   \label{fig:e912}
%% \end{figure*}

@@

Figure~\ref{fig:e912_2} show the resultant 1~Ry emissivity when the

@@

We fit this to the points shown in Figure~\ref{fig:e912_2} assuming a

@@

shown in both panels of Figure~\ref{fig:e912_2}.  We now comment on the

@@

and closed brown circles at $z=0$ in Figure~\ref{fig:e912_2}.  Our

@@

The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 1~Ry
emissivity model of \citet{2012ApJ...746..125H}, which based on the
bolometric luminosity function model of \citet{2007ApJ...654..731H}.
Their assumed emissivity agrees reasonably well with our
$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912_2}
shows the model presented by \citet{2015ApJ...813L...8M}.  This model
disagrees with ours rather severely at almost all redshifts in the
range considered here.  Note that a direct comparison with
\citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M} is
difficult because these models integrate the luminosity function to a
fixed fraction of the break luminosity $L_*$ instead of a fixed
absolute magnitude.  The chosen limite by \citet{2012ApJ...746..125H}
and \citet{2015ApJ...813L...8M} is $0.01L_*$.  Using a limit that
depends on the break luminosity can be problematic as different quasar
surveys used to develop these emissivity models often report
strikingly different break luminosity values.  Even when these samples
are homogeneized appropriately, have such an integration limit is only
justified if the faint-end slope of the luminosity function is
sufficiently shallow.

The grey dashed curve shows the emissivity model of
\citet{2017MNRAS.466.1160M}.  These authors integrate the luminosity
function down to $M_{1450}=-19$.  However, their model strongly
disagrees with our inference, potentially due to biases resulting from
combining binned luminosity function estimates from different sources
inhomogeneously.  The green curves in Figure~\ref{fig:e912_2} show the
luminosity function derived from a variability-selected sample
observed using the Sloan telescope and the Multiple Mirror Telescope
(MMT) by \citet{2013A&A...551A..29P}.  This sample of 1877 quasars
does not overlap with the variability-selected sample reported by the
BOSS survey \citep{2013ApJ...773...14R}.  \citet{2013A&A...551A..29P}
assum constant luminosity function slopes with a break at $z=2.2$ and
assume a pure luminosity evolution.  This leads to a discontinuity in
the emissivity evolution in their model at $z=2.2$.  We convert their
$g$-band magnitudes to $M_{1450}$ and integrate the resultant
luminosity function down to our two chosen integration limits.  The
result is shown in Figure~\ref{fig:e912_2} by the solid and dashed
orange curves, which correspond to $M_{1450}<-21$ and $-18$,
respectively.  For $M_{1450}<-21$, our models are in reasonable
agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
models disagree by 10--30\%.  Figure~\ref{fig:e912_2} also shows the
model presented by \citet{2016A&A...587A..41P}.  We consider their
PLE$+$LEDE model, in which the faint-end slope is assumed to stay
constant with redshift.  Although the emissivity evolution in this
model is continuous at $z=2.2$, it is not smooth.  This model agrees
with our $M_{1450}<-18$ result to a better degree relative to the
\citet{2013A&A...551A..29P} model.  We also compare our result with
the PLE$+$LEDE luminosity function model presented by
\citet{2017A&A...608A..64C} by reanalysing the
\citet{2016A&A...587A..41P} sample with an improved $K$-correction
implementation.  \citet{2017ApJ...847L..15O} recently fit a double
power law luminosity function model to a combined binned samples of
\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
photometric redshift $z\sim 6$ reported by
\citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
orange rectangle in Figure~\ref{fig:e912_2}.  The lower side of the
rectangle corresponds to the emissivity for the
\citet{2017ApJ...847L..15O} model excluding the
\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
the emissivity is higher; this is shown by the upper end of the
rectangle.  The open rectangle corresponds to $M_{1450}<-18$ and the
closed rectangle corresponds to $M_{1450}<-21$.

The red open cirles with error bars in Figure~\ref{fig:e912_2} show the
determination from the fits of \citet{2015AA...578A..83G}.  These
authors also choose a break luminosity-dependent integration limit of
$0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their model.
The resultant emissivities are factors of 2 to 3 higher than our
determinations for $z=4$--$6$.  This is puzzling at first sight,
because the AGN candidates reported by \citet{2015AA...578A..83G} are
consistent with our luminosity function estimates obtained without
these candidates (see Appendix~\ref{sec:conv}).  Our luminosity
function are also somewhat steeper than those reported by
\citet{2015AA...578A..83G}.  The discrepancy is explained by the
difference in the two luminosity function models at intermediate
magnitudes.  We find that the data prefer a much brighter break
luminosity than that infered by \citet{2015AA...578A..83G}.  This
reduces our emissivities relative to their estimates.  We go into this
issue in further detail in Appendix~\ref{sec:conv}.

\citet{2018AJ....155..131M} recently extended their previous Stripe~82
AGN sample by 1.5 magnitude and fit a double power law luminosity
function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
LF to our cosmology and assumed our SED obtain the emissivities shown
by the green circles in Figure~\ref{fig:e912_2}.  Again the open and
filled circles corresponds to our two integration limits.  Our
emissivity agrees with the measurement of \citet{2018AJ....155..131M}
for $M_{1450}<-21$ but is higher than their measurement for
$M_{1450}<-18$, which is not surprising due to the difference in the
luminosity function slopes.  The emissivity derived from the
luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
in Figure~\ref{fig:e912_2}.  These authors report 1668 AGN candidates at
$3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
faint-end slope is very flat ($\beta=-1.3\pm 0.05$), inconsistent with
our determination at all redshifts.  Their inferred emissivity is
consistent with our estimate for $M_{1450}\sim -21$.  Their emissivity
does not change significantly with the integration limit thanks to the
shallow slope.  We also compare our emissivities with the
determinations reported by \citet{2012ApJ...755..169M} at $z\sim 3.2$
and $z\sim 4$.  Their emissivity in reasonably agreement with our
model for $M_{1450}<-21$ at $z\sim 3.2$.  But their $M_{1450}<-18$
emissivity disagrees with all other high-redshift estimates, possibly
indicating a systematic error.  Our emissivity estimates are in good
agreement with those of \citet{2018MNRAS.474.2904P}.  Mention
Bongiorno.

@@

\subsection{Photon underproduction at $z=0$?}
% Kollmeier number of ~10 times higher than HM12 in figure.

It is instructive to closely examine if the corresponding hydrogen
photoionization rate is consistent with the \HI\ column density
distribution function measured from the \lya\ forest
\citep{2016ApJ...817..111D} at low redshifts ($z<0.5$).
\citet{2014ApJ...789L..32K} argued that in order to match the
\HI\ column density distribution function observed by
\citet{2016ApJ...817..111D} at these redshifts, hydrodynamical
cosmological simulations require a hydrogen photoionization rate that
is a factor of five larger than that in the UV background model of
\citet{2012ApJ...746..125H}.  Several recent studies have addressed
this `photon underproduction crisis' \citep{2015MNRAS.451L..30K,
  2015ApJ...811....3S, 2017MNRAS.467.3172G, 2017MNRAS.467.4802F,
  2017MNRAS.466..838G, 2017MNRAS.467L..86V}.  On the one hand, these
studies emphasised the uncertainty in the \citet{2012ApJ...746..125H}
UVB model at these redshifts due to the lack of certainty in the UV
photon emissivities of galaxies and AGN \citep{2015MNRAS.451L..30K,
  2015ApJ...811....3S}.  On the other hand, they noted the uncertainty
in the results of the cosmological simulations at these redshifts, due
to effects such as AGN feedback and limited numerical resolution
\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
  2017ApJ...835..175G}.  A general conclusion of these studies was
that the discrepancy between the photoionization rate required by the
observed \HI\ column density distribution and predicted by the UVB
model of \citet{2012ApJ...746..125H} is likely to be smaller than that
found by \citet{2014ApJ...789L..32K}.

%% The discrepancy is about a
%% factor of two instead of five.

\begin{figure}
  \begin{center}
    % rtg2.draw_g_puc()
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Evolution of the hydrogen photoionisation rate at low
    redshifts, when the AGN luminosity function is integrated down to
    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
    (red curve and shaded region).  Shaded regions show the one-sigma
    (68.26\%) uncertainty.  Also shown are the models and inferences
    from \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
    contribution in this model (dashed grey), \citet[dotted
      green]{2015ApJ...813L...8M}, \citet[dashed
      black]{2015ApJ...811....3S}, the QSO contribution from the model
    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
      grey]{2017ApJ...837..106O}, \citet[dashed
      brown]{2018arXiv180104931P}, \citet[yellow
      box]{2017MNRAS.467.4802F}, \citet[black
      box]{2017MNRAS.467L..86V}, \citet[inverted
      triangle]{2013MNRAS.436.1023B},
    \citet[pentagon]{2014ApJ...789L..32K}, and
    \citet[circle]{2017MNRAS.467.3172G}. Note that we use the the
    \HI\ column density distribution model from
    \citet{2012ApJ...746..125H} to derive the photoionization rate.
    \label{fig:puc}}
\end{figure}

Figure~\ref{fig:puc} shows the evolution of the \HI\ photoionization
rate due to AGN in our model for luminosity function integration
limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that this
photoionization rate is derived by fitting the model from
Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
luminosity functions in various redshift bins.  While doing this, as
discussed above, redshift bins that were interpreted as being affected
by systematic errors were ignored.  As a result, the emissivity model
used in calculating the photoionization rate is an extrapolation at
$z<0.6$.  However, it is interesting to note that even if we disregard
the $z<0.6$ data due to systematic errors, the extrapolated
emissivities at these redshifts are consistent with the emissivities
calculated from our luminosity function fits to these data for either
of our chosen integration limits.  This can be seen in
Figure~\ref{fig:e912_2}.  We find that the low-redshift
\HI\ photoionization rate in our model is higher than that in the
\citet{2012ApJ...746..125H} UVB model by a factor of 1.2 for
$M_{1450}<-21$ and a factor of 2 for $M_{1450}<-18$.  The
photoionization rate obtained when the faint AGN ($M_{1450}<-18$) are
included is consistent with a variety of recent estimates.  This rate
is in reasonable agreement with the photoionization rate found by
\citet{2017MNRAS.467.3172G}, who found that this photoionisation rate
is sufficient to explain the \HI\ column density distribution measured
by \citet{2016ApJ...817..111D}, thus alleviating the photon
underproduction problem without requiring additional contribution of
hydrogen-ionizing photons from galaxies.  At $z<0.5$, this
photoionization rate evolution in our model appears consistent also
with that derived by \citet{2015MNRAS.451L..30K} using the quasar
luminosity function measurements of \citet{2009MNRAS.392...19C} and
\citet{2013A&A...551A..29P}, although the evolution is somewhat
shallower in our model at $z>0.5$.  The model of
\citet{2015ApJ...813L...8M} also agrees with our $M_{1450}<-18$
inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
\HI\ column density distribution measurements to cosmological
simulations with an enhanced photoionization rate relative to the
\citet{2012ApJ...746..125H} model to find that
$\Gamma_\mathrm{HI}=4.6\times 10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$
produces the observed \HI\ column densities.  This photoionization
rate was achieved in the simulations of \citet{2015ApJ...811....3S} by
a combination of quasars and galaxies (with an escape fraction of
hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
seen in Figure~\ref{fig:puc}, this photoionization rate agrees with
our model at $z\sim 0$ for $M_{1450}<-18$, although it evolves
somewhat more rapidly at higher redshifts.  The photoionization rate
estimate by \citet{2017MNRAS.467.4802F} from the H$\alpha$ surface
brightness of a $z\sim 0$ galaxy observed by VLT/MUSE is somewhat
higher than even our $M_{1450}<-18$ determination.  However, it is
possible that the \citet{2017MNRAS.467.4802F} estimate is an upper
limit, as the contribution of local sources to the photoionization
rate is neglected in their modelling.  The requirement of an enhanced
photoionization rate at $z\sim 0$ relative to
\citet{2012ApJ...746..125H} UVB model is also confirmed by the
simulations presented by \citet{2017MNRAS.467L..86V},
\citet{2017ApJ...837..106O}, and \citet{2018arXiv180104931P}.  But
note that, as discussed above in Section~\ref{sec:e912}, a direct
comparison of our results with the models of
\citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K}, and
\citet{2018arXiv180104931P} is difficult because of the inhomogenous
redshift-dependent integration limits adopted by these authors.

@@

\begin{figure}
  \begin{center}
    % qhe.py 
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Evolution of the \HeIII\ ionization fraction in our model,
    when the AGN luminosity function is integrated down to
    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
    (red curve and shaded region).  The shaded regions show the
    one-sigma (68.26\%) uncertainty.  Other curves show models of
    \citet[solid grey]{2012ApJ...746..125H}, \citet[dashed
      grey]{2015ApJ...813L...8M}, \citet[brown with shaded
      region]{2016ApJ...828...90L}, \citet[blue]{2018arXiv180104931P},
    \citet[maroon]{2009ApJ...694..842M}, and
    \citet[green]{2014MNRAS.445.4186C}.  Note that we derive
    $Q_\nHeIII$ using Equation~(\ref{eqn:qHedot}), which ignores the
    presence of \HeII\ Lyman-limit systems and becomes inaccurate
    towards $Q_\nHeIII\sim 1$. \label{fig:qhe}}
\end{figure}

@@

\section{Comparison with G15}
\label{sec:conv}
%% Define 'G15' somewhere above.
In the double power law luminosity function models presented in
distinct redshift bins in Section~\ref{sec:bins}, we did not include
the 19 low-luminosity ($M_{1450}>-22.6$) AGN between redshifts $z=4.1$
and $6.3$ reported by G15.  While this was done in order to restrict
our sample to quasars with spectroscopic redshift determinations, it
is instructive to consider how our results are affected if the G15 AGN
are added to the analysis.  In their work, G15 found a shallower
faint-end slope ($\beta\sim -1.5$ to $-1.8$) for the luminosity
function at $4.1 < z < 6.3$, relative to our result from other AGN
samples at these redshifts ($\beta\sim -2.0$ to $-2.5$).  Still, G15
derived a higher 912\,\AA\ emissivity than our estimates
(cf.\ Figure~\ref{fig:e912_2}), so that in their analysis AGN can
produce all ionizing photons necessary to keep hydrogen ionized and
explain the \lya data.  The black points in
Figure~\ref{fig:params_giallongo} show the parameters of the double
power law luminosity function from our analysis of
Section~\ref{sec:bins}.  The red open circles show the parameter
values obtained when the G15 sample is added to the analysis.  We find
that the two results are highly consistent, showing that the G15
sample is consistent with our double power law fit obtained from other
AGN samples are comparable redshifts.  This is surprising as the
integrated 912\,\AA\ emissivities in our model are smaller than those
derived by G15.  Figure~\ref{fig:lf_giallongo} provides an
explanation.  As seen in this figure, the double power law fits
favoured by G15 (red dashed curves) are quite different from our fits
(black curves).  The characteristic luminosity $M_*$ obtained by G15
is much fainter ($\sim -23$ at $z = 5$) than that resulting out of our
analysis ($\sim -29$ at $z = 5$).  Thus the 912\,\AA\ emissivities are
enhanced in G15 because of the increase contribution from
intermediate-luminosity AGN in their model.
Figure~\ref{fig:lf_giallongo} suggests that this is possibly because
of the inclusion of SDSS Stripe 82 data from
\citet{2013ApJ...768..105M} and the AGN samples of
\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in our
analysis.  Additionally, the homogenisation of data in our work may
also cause part of the difference.

\begin{figure*}
  \begin{center}
    % summary_giallongo.py
    \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
  \end{center}
  \caption{Effect of the 19 AGN reported by \citet{2015AA...578A..83G}
    on the best-fit double power law luminosity function parameters in
    redshift bins from $z=0$ to $7$.  Black points show parameter
    values from Figure~\ref{fig:evoln}.  Red open circles show the
    parameter values obtained when the sample of G15 is added to the
    analysis.  In both cases, vertical error bars show one-sigma
    (68.26\%) uncertainties, and horizontal error bars show widths of
    the redshift bins. \label{fig:params_giallongo}}
\end{figure*}
